Further Evidence of Modified Spin-down in Sun-like Stars:\\Pile-ups in the Temperature--Period Distribution

### 2022-03-21 src/ms.tex
detection bias discussion

\subsection{Detection biases}
\edit1{To this point, we have not addressed the detection biases inherent to Kepler rotation period catalogs. As rotation periods become longer, it becomes more difficult to measure periods directly from rotational brightness modulations in Kepler time series. This is true for at least three reasons: (1) the Kepler baseline is finite, (2) photometric variation amplitude declines with increasing rotation period, and (3) photometric variations tend to become less periodic with increasing rotation period.
\citet{vanSaders2019} addressed this issue in detail...}

>>>>

\subsection{Detection biases}
\edit1{To this point, we have not addressed the detection biases inherent to Kepler rotation period catalogs. As rotation periods become longer, it becomes more difficult to measure periods directly from rotational brightness modulations in Kepler time series. This is true for at least three reasons: (1) the Kepler baseline is finite, (2) photometric variation amplitude declines with increasing rotation period, and (3) photometric variations tend to become less periodic with increasing rotation period.}

\edit1{\citet{vanSaders2019} addressed this issue in detail, finding that a threshold of Ro$_\mathrm{thresh} \approx 2$ could reproduce the observed upper edge of the \citet{McQuillan2014} \teff–\prot distribution. However, those authors presented two arguments that suggest detection bias is not solely responsible for producing the observed \teff–\prot distribution. First, stars at the upper edge are not those with the lowest-amplitude signals detected, as one would expect from a detection edge. For the variability amplitudes typical of Sun-like stars at the upper edge, one finds cooler stars with similar amplitude at even longer periods, as well as hotter stars with much smaller amplitudes (though at shorter periods). Even among Sun-like stars, those authors found that 9\% of stars below the edge have amplitudes smaller than stars with similar \teff at the edge (possibly due to issues such as flux dilution).}

\edit1{Critically, we also note that while an Ro-dependent detection threshold may reproduce the upper edge of the \teff–\prot distribution, it would not be responsible for producing a pile-up or overdensity at this edge. To our knowledge, there are no systematics of the rotation period catalogs considered here that would bias stars towards the detection threshold.}
